Considering scale in multilayer animal social networks

### 2020-08-26 paper/manuscript.Rmd
eg fine scale

### Spatial scale
To assess the influence of land cover spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales 
(100 - 1000 m by steps of 100 m) using a modal moving window method [@Graham_2019a]. 
We assume 30 m and 100 m represents fine-scale decision making
for caribou, while 500 - 1000 m represents the scale at which
caribou tend to select and avoid habitat [@Bastille_2018]. Multilayer networks
consisted of the social associations between `r DT[, uniqueN(get(idcol))]`
individuals across three habitat layers (foraging, forest and open) for the
entire study period. For each land cover resolution, we calculated individual
graph strength within each habitat layer, and edge overlap and multidegree
across habitat layers.

>>>>

### Spatial scale
To assess the influence of land cover spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales 
(100 - 1000 m by steps of 100 m) using a modal moving window method [@Graham_2019a]. 
We assume 30 m and 100 m represents fine-scale decision making
for caribou [@Mayor_2007], while 500 - 1000 m represents the scale at which
caribou tend to select and avoid habitat [@Bastille_2018]. Multilayer networks
consisted of the social associations between `r DT[, uniqueN(get(idcol))]`
individuals across three habitat layers (foraging, forest and open) for the
entire study period. For each land cover resolution, we calculated individual
graph strength within each habitat layer, and edge overlap and multidegree
across habitat layers.
